\documentclass[8pt,twocolumn]{article}
\input{../typesetting.tex}
\author{Yingbo Ma \thanks{Student ID: \tt{16058474}}}
\title{\vspace{-1.cm}Homework 5}
\date{May 15, 2018}

\begin{document}
\maketitle

\begin{Answer}[number=29]
  \emph{16.1.29:}
  The function $f(x,y) = x^2 + y^2$ has the gradient $\grad f(x,y) =
  \mqty[2x\\2y]$. All the vectors point away from the origin.
  Thus $\grad f$ corresponds to graph \RC3.

  \emph{16.1.30:}
  The function $f(x,y) = x(x+y)$ has the gradient $\grad f(x,y) =
  \mqty[2x+y\\x]$. The vectors point upward when $x>0$, and vectors point
  downward when $x<0$.
  Thus $\grad f$ corresponds to graph \RC4.

  \emph{16.1.31:}
  The function $f(x,y) = (x+y)^2$ has the gradient $\grad f(x,y) =
  \mqty[2x+2y\\2x+2y]$. The vectors vanish along the line $y=-x$.
  Thus $\grad f$ corresponds to graph \RC2.

  \emph{16.1.32:}
  The function $f(x,y) = \sin \sqrt{x^2+y^2}$ has the gradient $\grad f(x,y) =
  \frac{\cos\sqrt{x^2+y^2}}{\sqrt{x^2+y^2}}\mqty[x\\y]$. The magnitude of
  vectors changes periodically as its distance grows from the origin.
  Thus $\grad f$ corresponds to graph \RC1.

  \emph{16.2.17:}
  \begin{enumerate}
    \item
      The function $\bm{F}$ have positive $y$-component along the line $x=-3$, and
      since the path goes upward, the integrand of the integral
      $\int_{C_1}\bm{F}\cdot \dd{\bm{r}} = \int_{C_1}\bm{F}\cdot\bm{T} \dd{s}$ always
      stay positive, thus the line integral is also positive.
    \item
      The function $\bm{F}$ goes in a clockwise fashion, while the curve $C_2$
      goes counterclockwise, and they are opposite. Thus the value of the line
      integral must be negative.
  \end{enumerate}

  \emph{16.2.8:}
  Let $C = C1 + C2$ and we have $C_1: x=2\cos t, y=2\sin t, 0\le t \le
  \frac{pi}{2}$ and $C_2: x=4t, y=t+2, 0\le t\le 1$. We then have the integral
  \begin{align*}
    \int_C x^2\dd{x}+y^2\dd{y} &= \int_{C_1} x^2\dd{x}+y^2\dd{y} + \int_{C_2}
    x^2\dd{x}+y^2\dd{y} \\
    &= \int_0^{\frac{\pi}{2}}(2\cos t)^2 (-2\sin t\dd{t}) \\
    &+ (2\sin t)^2 (2\cos t\dd{t}) + \int_0^1 (4t)^2 4\dd{t} + (t+2)^2 \dd{t}
    \\
    &= \int_0^{\frac{\pi}{2}}8 (\sin^2 t \cos t - \cos^2 t\sin t)\dd{t} \\
    &+\int_0^1 65t^2+4t+4 \dd{t}
  \end{align*}
\end{Answer}

\begin{Answer}[number=30]
  Let $f(x,y)=x^2y$ and let $\bm{F}(x,y)=\grad f(x,y) = \mqty[2xy\\ x^2]$. We
  have $C_1: x=2t, y=4t, 0\le t\le 1$ and $C_2: x=2t, y=4t^2, 0\le t\le 1$. We
  have
  \begin{align*}
    \int_{C_1} \bm{F}\cdot \dd{\bm{r}} &= \int_{C_1} 2xy \dd{x} + x^2\dd{y} \\
    &= \int_0^1 2(2t)(4t) 2\dd{t} + (4t)^2 4\dd{t} = 16\int_0^1 3t^2\dd{t} \\
    &=16 \eval{t^3}_0^1 = 16
  \end{align*}
  and
  \begin{align*}
    \int_{C_2} \bm{F}\cdot \dd{\bm{r}} &= \int_{C_2} 2xy \dd{x} + x^2\dd{y} \\
    &= \int_0^1 2(2t)(4t^2) 2\dd{t} + (2t^2)^2 8t\dd{t} = \int_0^1 32t^3 + 32t^3\dd{t} \\
    &= 16\int_0^1 4t^3 \dd{t} = 16 \eval{t^4}_0^1 = 18.
  \end{align*}
  Thus, \(\int_{C_2} \bm{F}\cdot \dd{\bm{r}}\) and \(\int_{C_1} \bm{F}\cdot
  \dd{\bm{r}}\) have the same value.
\end{Answer}

\begin{Answer}[number=31]
  \begin{itemize}
    \item
      \input{fig.tex}
      \item
        Such parametric equation can be $x(t) = 1, y(t)=t^2/2$ which has the
        tangent vector $\mqty[1\\ t_0]$ at $t_0$, which is parallel to the
        vector field $\eval{\bm{F}(x,y)}_{t_0}=\mqty[1\\t_0]$. Also, since the
        parametric equation passes the point $(8,15)$, the parametric equation
        is then $x(t)=t, y(t)=\frac{t^2}{2}-17$.
    \item
      \begin{proof}
        Assume toward contradiction. There exists a smooth function $f(x,y)$
        such that we have the equality $\nabla f=\bm{F}$. We then have
        $\pdv{f}{x}=1,$ and $\pdv{f}{y}=x$. When $x=2$ apply the chain rule, we get
        \[
          \eval{\pdv{f}{x}}_{x=2} = \eval{\pdv{f}{y}\pdv{y}{x}}_{x=2} =
          \eval{x\cdot 1}_{x=2} = 2.
        \]
        However, the above result is not $1$, the value of $\pdv{f}{x}$ that we
        obtained earlier. This is a contradiction. Hence, there does not exist
        a smooth function $f(x,y)$ such that the equality $\nabla f=\bm{F}$
        holds. This completes the proof.
      \end{proof}
  \end{itemize}
\end{Answer}

\begin{Answer}[number=32]
  \input{fig1.tex}
  \begin{proof}
    Since the function $f(x,y)$ is a concious function, the function $g(x,y)$
    such that $\dv{t}g(x(t),y(t)) = f(x,y)$ holds for all $t$ in real number.
    Then, we have
    \[
      \int_C f(x,y) \dd{s} = g(x_1,y_1) - g(x_0, y_0) = g(7,0) - g(2,0),
    \]
    where $(x_1,y_1)$ and $(x_0, y_0)$ are the end points of the curve $C$.
    Also, we have
    \[
      \int_2^7 f(x,0) \dd{x} = g(7, 0) - g(2, 0),
    \]
    for the right hand side of the equation. Hence $\int_C f(x,y) \dd{s} =
    \int_2^7 f(x,0) \dd{x}$ holds. This completes the proof.
  \end{proof}
\end{Answer}

\end{document}
